Compared to all other algorithms for integer factorization, it is clear that Shor's algorithm on a quantum computer performs more efficiently than other classical counterparts. Shor's algorithm express the idea that quantum computers are capable of performing tasks with lower complexity than classical ones and its implementation further verifies it. Despite the success in implementing the algorithm, quantum computers available today are far away at making themselves approachable and advantageous for the general public. The current status of quantum computers does not allow scalable and applicable use of Shor's algorithm. Many types of research and efforts have been made in the field to make use of the algorithm. \par

Despite the reality that current quantum computers are not able to make use of  Shor's algorithm, the introduction of Shor's algorithm itself has a profound effect on science. It popularized the concept of quantum computation to the research community and public and helped in further exploration of more capabilities and possibilities in quantum information/computation. This algorithm is one of the reasons that quantum computation and information is considered as one of the most promising fields of time. Quantum computing is expected to be the future of computing. It is highly likely that quantum computing and information will have remarkable applications in our lives directly or indirectly. Research, simulation, optimization, and security are some of the promising areas of the application of quantum computers.\par